Hospital Information Technology and Physician Response

### 2022-08-23 Table Code/split stats.tex

\begin{table}[h]

\caption{Means by Age Sample}
\centering
\begin{tabular}[t]{lccc}
\toprule
Variable & Age $>$ 60 & Age $<=$ 60 & Any Who Retire\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Outcomes}}\\
\hspace{1em}Ever Retire & 0.02 & 0.02\\
\hspace{1em}Fraction Patients in Office & 0.44 & 0.27 \\
\hspace{1em}Work in an Office & 0.78 & 0.52 \\
\hspace{1em}Change Zip Codes & 0.06 & 0.09 \\
\hspace{1em}Number of Patients & 431.96 & 357.46 \\
\hspace{1em}Claim Count & 3216.46 & 2019.17\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Treatment}}\\
\hspace{1em}Exposure to an EHR & 0.77 & 0.76 & 0.77\\
\hspace{1em}Fraction of Hospitals with EHR & 0.60 & 0.63 & 0.64\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Characteristics}}\\
\hspace{1em}Age & 61.07 & 44.06 & 48.29\\
\hspace{1em}Female & 0.15 & 0.35 & 0.39\\
\hspace{1em}Number of Hospitals Worked With & 1.67 & 1.53 & 1.35\\
\hspace{1em}Number of Systems Worked With & 1.40 & 1.33 & 1.19\\
\bottomrule
\end{tabular}
\label{tab:splitstats}
\end{table}

>>>>

\begin{table}[ht]

\caption{Means by Age Sample}
\centering
\begin{tabular}[t]{lcc}
\toprule
Variable & Age $>$ 60 & Age $<=$ 60\\
\midrule
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Outcomes}}\\
\hspace{1em}Ever Retire & 0.04 & 0.03\\
\hspace{1em}Fraction Patients in Office & 0.15 & 0.09\\
\hspace{1em}Work in an Office & 0.48 & 0.28\\
\hspace{1em}Change Zip Codes & 0.10 & 0.12\\
\hspace{1em}Number of Patients & 342 & 329\\
\hspace{1em}Claim Count & 1,767 & 1,332\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Treatment}}\\
\hspace{1em}Exposure to an EHR & 0.76 & 0.75\\
\hspace{1em}Fraction of Hospitals with EHR & 0.59 & 0.64\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Characteristics}}\\
\hspace{1em}Age & 60.31 & 42.75\\
\hspace{1em}Female & 0.18 & 0.36\\
\hspace{1em}Number of Hospitals Worked With & 1.63 & 1.48\\
\hspace{1em}Number of Systems Worked With & 1.38 & 1.30\\
\bottomrule
\end{tabular}
\end{table}
\label{tab:splitstats}
